---
title: "Interneuron heatmaps"
output: html_document
date: '2022-11-28'
editor_options: 
  chunk_output_type: console
---
```{r}
library(pheatmap)
library(clusterProfiler)
library(org.Mm.eg.db)
```

read in tables
```{r}
Nkx.foxg1.IN.intersection<- read.table("C:/Users/ia1014/Downloads/nkx2creDot1lcKO_rnaseq/Intersected DEG NkxVT-Foxg1_Intersection IN markers.txt", 
                                header=TRUE, sep="\t", quote="", fill=TRUE, row.names = "symbol")

Nkx.foxg1.padj.intersection<- read.table("C:/Users/ia1014/Downloads/nkx2creDot1lcKO_rnaseq/Intersection DEGs NkxVT_Foxg1 padj 0.05.txt", 
                                header=TRUE, sep="\t", quote="", fill=TRUE, row.names = "symbol")

Nkx.sst.pv.intersection<- read.table("C:/Users/ia1014/Downloads/nkx2creDot1lcKO_rnaseq/Nkx-vT_SST and PV markers for heatmap_annotated.txt", 
                                header=TRUE, sep="\t", quote="", fill=TRUE, row.names = "symbol")

Nkx.postmit.intersection<- read.table("C:/Users/ia1014/Downloads/nkx2creDot1lcKO_rnaseq/Nkx-vT_Postmitotic neuronal markers for heatmap_.txt", 
                                header=TRUE, sep="\t", quote="", fill=TRUE, row.names = "symbol")
Nkxdot.vt.progenitor<-read.table("C:/Users/ia1014/Downloads/nkx2creDot1lcKO_rnaseq/nkxdot-vt-progenitor markers.txt", 
                                header=TRUE, sep="\t", quote="", fill=TRUE, row.names = "symbol")

Foxg1dot.in<-read.table("C:/Users/ia1014/Downloads/nkx2creDot1lcKO_rnaseq/221219 Foxg1 DEG IN markers Norm counts  - simplied.txt", 
                                header=TRUE, sep="\t", quote="", fill=TRUE, row.names = "symbol", dec = ".")


morphogen<- read.table("C:/Users/ia1014/Downloads/Morphogens_heatmap.txt", 
                                header=TRUE, sep="\t", quote="", fill=TRUE, row.names = "symbol")

```

### heatmap of intersected DEGs in Nkx and Foxg1 DOT1L cKO models and interneuron markers
```{r, fig.align='center', fig.height=5, fig.width=4}
Nkx.foxg1.IN.intersection$Nkx.log2FoldChange<-as.numeric(gsub(",", ".", Nkx.foxg1.IN.intersection$Nkx.log2FoldChange))
Nkx.foxg1.IN.intersection$Foxg1log2FoldChange<-as.numeric(gsub(",", ".", Nkx.foxg1.IN.intersection$Foxg1log2FoldChange))
    
Nkx.foxg1.IN.intersection<- as.matrix(Nkx.foxg1.IN.intersection)
nkx.foxg1.IN.heatmap<- pheatmap(Nkx.foxg1.IN.intersection,
                                cluster_cols = F, 
                                border_color = "white", 
                                cellwidth = 10,
                                cellheight = 10,
                                clustering_distance_rows = "euclidean",
                                color = hcl.colors(80, "RdBu", rev=TRUE, fixup = T),
                                angle_col = 45,
                                fontsize = 8, 
                                show_colnames = T, 
                                show_rownames = T
                                        )
pdf("C:/Users/ia1014/Downloads/nkx2creDot1lcKO_rnaseq/281122_nkx_foxg1_interneuron_intersection_heatmap.pdf", 
    width=4, 
    height=4)
print(nkx.foxg1.IN.heatmap)
dev.off()
```

### heatmap of intersected DEGs in Nkx and Foxg1 DOT1L cKO models
```{r, fig.align='center', fig.height=40, fig.width=4}
Nkx.foxg1.padj.intersection$Nkx.log2FoldChange<-as.numeric(gsub(",", ".", Nkx.foxg1.padj.intersection$Nkx.log2FoldChange))
Nkx.foxg1.padj.intersection$Foxg1log2FoldChange<-as.numeric(gsub(",", ".", Nkx.foxg1.padj.intersection$Foxg1log2FoldChange))
    
Nkx.foxg1.padj.intersection<- as.matrix(Nkx.foxg1.padj.intersection)
nkx.foxg1.padj.heatmap<- pheatmap(Nkx.foxg1.padj.intersection,cluster_cols = F, 
                                       border_color = "white", 
                                         cellwidth = 6,
                                        cellheight = 6,
                                       clustering_distance_rows = "euclidean", 
                                       color = hcl.colors(80, "RdBu", rev=TRUE, fixup = T),
                                       angle_col = 45, 
                                       fontsize = 7, show_colnames = T, show_rownames = T
                                        )
pdf("C:/Users/ia1014/Downloads/nkx2creDot1lcKO_rnaseq/201222_nkx_foxg1_padj_intersection_heatmap.pdf", 
    width=4, 
    height=14.5)
print(nkx.foxg1.padj.heatmap)
dev.off()
```
### GO-terms of the Nkx and Foxg1 Dot1l cKO models DEG intersection

```{r}
# run GO-term enrichment analysis
nkx.foxg1.deg.list<-rownames(Nkx.foxg1.padj.intersection)
nkx.foxg1.deg.list<-bitr(nkx.foxg1.deg.list, fromType = "SYMBOL", toType = "ENTREZID", drop = T, OrgDb = "org.Mm.eg.db")
nkx.foxg1.intersection.GO<-enrichGO(nkx.foxg1.deg.list$ENTREZID, 
                                     OrgDb = "org.Mm.eg.db", 
                                     ont = "BP", 
                                     pAdjustMethod = "BH", 
                                     qvalueCutoff = 0.05,
                                     pvalueCutoff = 0.05, 
                                     readable = TRUE)
# simplify terms to avoid redundancy
nkx.foxg1.intersection.GO.simp <- simplify(nkx.foxg1.intersection.GO, 
                                           cutoff = 0.5, 
                                           by = "p.adjust", 
                                           select_fun = min,
                                           measure = "Wang",
                                           semData = NULL)

# Dotplot of differential GO terms

dp.nkx.foxg1 = dotplot(nkx.foxg1.intersection.GO,
                       showCategory = 12,
                       font.size = 10 )
dp.nkx.foxg1

pdf("C:/Users/ia1014/Downloads/nkx2creDot1lcKO_rnaseq/nkx_foxg1_intersection_GOterms_BP.pdf",
    width = 5, height = 5)
print(dp.nkx.foxg1)
dev.off()
```

### heatmap of intersected DEGs in Nkx DOt1lcKO and sst and PV markers
```{r, fig.align='center', fig.height=20, fig.width=4}
Nkx.sst.pv.intersection.df<-Nkx.sst.pv.intersection[, (4:12)]
Nkx.sst.pv.annotation<-Nkx.sst.pv.intersection[,-(1:12)]
Nkx.sst.pv.annotation<-as.data.frame(Nkx.sst.pv.annotation)
Nkx.sst.pv.intersection.df$WT1<-as.numeric(gsub(",", ".", Nkx.sst.pv.intersection.df$WT1))
Nkx.sst.pv.intersection.df$WT2<-as.numeric(gsub(",", ".", Nkx.sst.pv.intersection.df$WT2))
Nkx.sst.pv.intersection.df$WT3<-as.numeric(gsub(",", ".", Nkx.sst.pv.intersection.df$WT3))
Nkx.sst.pv.intersection.df$WT5<-as.numeric(gsub(",", ".", Nkx.sst.pv.intersection.df$WT5))
Nkx.sst.pv.intersection.df$KO1<-as.numeric(gsub(",", ".", Nkx.sst.pv.intersection.df$KO1))
Nkx.sst.pv.intersection.df$KO2<-as.numeric(gsub(",", ".", Nkx.sst.pv.intersection.df$KO2))
Nkx.sst.pv.intersection.df$KO3<-as.numeric(gsub(",", ".", Nkx.sst.pv.intersection.df$KO3))
Nkx.sst.pv.intersection.df$KO4<-as.numeric(gsub(",", ".", Nkx.sst.pv.intersection.df$KO4))
Nkx.sst.pv.intersection.df$KO5<-as.numeric(gsub(",", ".", Nkx.sst.pv.intersection.df$KO5))
rownames(Nkx.sst.pv.annotation)<-rownames(Nkx.sst.pv.intersection.df)
Nkx.sst.pv.intersection.df<- as.matrix(Nkx.sst.pv.intersection.df)
Nkx.sst.pv.intersection.heatmap<- pheatmap(Nkx.sst.pv.intersection.df,cluster_cols = F, 
                                           annotation_row = Nkx.sst.pv.annotation,
                                           annotation_names_row = F, cluster_rows = F,
                                           border_color = "white", 
                                         cellwidth = 10,
                                        cellheight = 10,
                                         color = hcl.colors(80, "RdBu", rev=TRUE, fixup = T),
                                       angle_col = 45, 
                                       fontsize = 8, show_colnames = T, show_rownames = T, scale = "row"
                                        )
pdf("C:/Users/ia1014/Downloads/nkx2creDot1lcKO_rnaseq/281122_nkx_sst_pv_marker_intersection_heatmap_clustered.pdf", 
    width=4, 
    height=5)
print(Nkx.sst.pv.intersection.heatmap)
dev.off()
```

### heatmap of intersected DEGs in Nkx DOt1lcKO and post-mitotic markers
```{r, fig.align='center', fig.height=20, fig.width=4}
Nkx.postmit.intersection<-Nkx.postmit.intersection[, (3:11)]
Nkx.postmit.intersection$WT1<-as.numeric(gsub(",", ".", Nkx.postmit.intersection$WT1))
Nkx.postmit.intersection$WT2<-as.numeric(gsub(",", ".", Nkx.postmit.intersection$WT2))
Nkx.postmit.intersection$WT3<-as.numeric(gsub(",", ".", Nkx.postmit.intersection$WT3))
Nkx.postmit.intersection$WT5<-as.numeric(gsub(",", ".", Nkx.postmit.intersection$WT5))
Nkx.postmit.intersection$KO1<-as.numeric(gsub(",", ".", Nkx.postmit.intersection$KO1))
Nkx.postmit.intersection$KO2<-as.numeric(gsub(",", ".", Nkx.postmit.intersection$KO2))
Nkx.postmit.intersection$KO3<-as.numeric(gsub(",", ".", Nkx.postmit.intersection$KO3))
Nkx.postmit.intersection$KO4<-as.numeric(gsub(",", ".", Nkx.postmit.intersection$KO4))
Nkx.postmit.intersection$KO5<-as.numeric(gsub(",", ".", Nkx.postmit.intersection$KO5))

Nkx.postmit.intersection<- as.matrix(Nkx.postmit.intersection)
Nkx.postmit.intersection.heatmap<- pheatmap(Nkx.postmit.intersection,cluster_cols = F, 
                                       border_color = "white", 
                                         cellwidth = 10,
                                        cellheight = 10,
                                       clustering_distance_rows = "euclidean", 
                                       color = hcl.colors(80, "RdBu", rev=TRUE, fixup = T),
                                       angle_col = 45, 
                                       fontsize = 8, show_colnames = T, show_rownames = T, scale = "row"
                                        )
pdf("C:/Users/ia1014/Downloads/nkx2creDot1lcKO_rnaseq/281122_nkx_postmit_intersection_heatmap.pdf", 
    width=4, 
    height=8)
print(Nkx.postmit.intersection.heatmap)
dev.off()
```

```{r}
sessionInfo()
```
### heatmap of intersection of Nkxdot VT p0.05 DEGs and progenitor markers
```{r}
Nkxdot.vt.progenitor<-read.table("C:/Users/ia1014/Downloads/nkx2creDot1lcKO_rnaseq/nkxdot-vt-progenitor markers.txt", 
                                header=TRUE, sep="\t", quote="", fill=TRUE, row.names = "symbol")

Nkxdot.vt.progenitor$WT1<-as.numeric(gsub(",", ".", Nkxdot.vt.progenitor$WT1))
Nkxdot.vt.progenitor$WT2<-as.numeric(gsub(",", ".", Nkxdot.vt.progenitor$WT2))
Nkxdot.vt.progenitor$WT3<-as.numeric(gsub(",", ".", Nkxdot.vt.progenitor$WT3))
Nkxdot.vt.progenitor$WT5<-as.numeric(gsub(",", ".", Nkxdot.vt.progenitor$WT5))
Nkxdot.vt.progenitor$KO1<-as.numeric(gsub(",", ".", Nkxdot.vt.progenitor$KO1))
Nkxdot.vt.progenitor$KO2<-as.numeric(gsub(",", ".", Nkxdot.vt.progenitor$KO2))
Nkxdot.vt.progenitor$KO3<-as.numeric(gsub(",", ".", Nkxdot.vt.progenitor$KO3))
Nkxdot.vt.progenitor$KO4<-as.numeric(gsub(",", ".", Nkxdot.vt.progenitor$KO4))
Nkxdot.vt.progenitor$KO5<-as.numeric(gsub(",", ".", Nkxdot.vt.progenitor$KO5))

Nkxdot.vt.progenitor<- as.matrix(Nkxdot.vt.progenitor)
Nkxdot.vt.progenitor.heatmap<- pheatmap(Nkxdot.vt.progenitor,
                                        cluster_cols = F, 
                                       border_color = "white", 
                                         cellwidth = 10,
                                        cellheight = 10,
                                       cluster_rows = T,
                                       clustering_distance_rows = "euclidean", 
                                       color = hcl.colors(80, "RdBu", rev=TRUE, fixup = T),
                                       angle_col = 45, 
                                       fontsize = 8, show_colnames = T, show_rownames = T, scale = "row"
                                        )
pdf("C:/Users/ia1014/Downloads/nkx2creDot1lcKO_rnaseq/281122_nkxdot_progenitor_intersection_heatmap.pdf", 
    width=4, 
    height=4)
print(Nkxdot.vt.progenitor.heatmap)
dev.off()

```
### heatmap of intersected DEGs in Foxg1.dotcko and interneuron markers
```{r, fig.align='center', fig.height=15, fig.width=4}
Foxg1dot.in$WT1<-as.numeric(gsub(",", ".", Foxg1dot.in$WT1))
Foxg1dot.in$WT2<-as.numeric(gsub(",", ".", Foxg1dot.in$WT2))
Foxg1dot.in$WT3<-as.numeric(gsub(",", ".", Foxg1dot.in$WT3))
Foxg1dot.in$WT4<-as.numeric(gsub(",", ".", Foxg1dot.in$WT4))
Foxg1dot.in$WT5<-as.numeric(gsub(",", ".", Foxg1dot.in$WT5))
Foxg1dot.in$KO1<-as.numeric(gsub(",", ".", Foxg1dot.in$KO1))
Foxg1dot.in$KO2<-as.numeric(gsub(",", ".", Foxg1dot.in$KO2))
Foxg1dot.in$KO3<-as.numeric(gsub(",", ".", Foxg1dot.in$KO3))
Foxg1dot.in$KO4<-as.numeric(gsub(",", ".", Foxg1dot.in$KO4))
Foxg1dot.in$KO5<-as.numeric(gsub(",", ".", Foxg1dot.in$KO5))
Foxg1dot.in<- as.matrix(Foxg1dot.in)
Foxg1dot.in.heatmap<- pheatmap(Foxg1dot.in,
                                cluster_cols = F, 
                                border_color = "white", 
                                cellwidth = 10,
                                cellheight = 10,
                                scale = "row",
                                clustering_distance_rows = "euclidean",
                                color = hcl.colors(80, "RdBu", rev=TRUE, fixup = T),
                                angle_col = 45,
                                fontsize = 8, 
                                show_colnames = T, 
                                show_rownames = T
                                        )
pdf("C:/Users/ia1014/Downloads/nkx2creDot1lcKO_rnaseq/221222_foxg1_interneuron_intersection_heatmap.pdf", 
    width=4, 
    height=13)
print(Foxg1dot.in.heatmap)
dev.off()
```

```{r}
### heatmap of intersected DEGs in Nkx DOt1lcKO and sst and PV markers

morphogen<-morphogen[, (3:11)]
morphogen<-morphogen[-c(15),]
morphogen<-as.data.frame(morphogen)
morphogen$WT1<-as.numeric(gsub(",", ".", morphogen$WT1))
morphogen$WT2<-as.numeric(gsub(",", ".", morphogen$WT2))
morphogen$WT3<-as.numeric(gsub(",", ".", morphogen$WT3))
morphogen$WT5<-as.numeric(gsub(",", ".", morphogen$WT5))
morphogen$KO1<-as.numeric(gsub(",", ".", morphogen$KO1))
morphogen$KO2<-as.numeric(gsub(",", ".", morphogen$KO2))
morphogen$KO3<-as.numeric(gsub(",", ".", morphogen$KO3))
morphogen$KO4<-as.numeric(gsub(",", ".", morphogen$KO4))
morphogen$KO5<-as.numeric(gsub(",", ".", morphogen$KO5))
morphogen<- as.matrix(morphogen)
morphogen.heatmap<- pheatmap(morphogen,cluster_cols = F, 
                                           annotation_names_row = T, cluster_rows = F,
                                           border_color = "white", 
                                         cellwidth = 10,
                                        cellheight = 10,
                                         color = hcl.colors(80, "RdBu", rev=TRUE, fixup = T),
                                       angle_col = 45, 
                                       fontsize = 8, show_colnames = T, show_rownames = T, scale = "row"
                                        )
pdf("C:/Users/admin.ia1014/Documents/DOT1L-interneuron-development/110423_IN_morphogen_heatmap.pdf", 
    width=4, 
    height=4)
print(morphogen.heatmap)
dev.off()
```

```

